### 2017-12-12 Paper/main.tex
Updates from ShareLaTeX

\documentclass[twocolumn]{article}
\usepackage{array,url,kantlipsum}
\usepackage{lmodern}
\usepackage{tikz}
\usepackage{capt-of}
\usepackage{biblatex}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{rotating}

@@

% \Mark is probably provided by spconf, that I don't have
\newcommand{\Mark}[1]{\textsuperscript{#1}}

@@

After the model setting we set a series of condition that create the signal. Such condition are highlighted in the following diagram.

@@

All the scripts and files are available on GitHub at the following repository:

>>>>

\documentclass[twocolumn]{article}
\usepackage{array,url,kantlipsum}
\usepackage{lmodern}
\usepackage{tikz}
\usepackage{capt-of}
\usepackage{biblatex}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{rotating}
\usepackage{hyperref}

@@

\documentclass[border=5mm,tikz,preview]{standalone}
    \usetikzlibrary{arrows, arrows.meta, 
                    chains,
                    positioning,
                    shapes}
\makeatletter
\tikzset{reset join/.code={\def\tikz@after@path{}}}
\makeatother

\newcommand{\Mark}[1]{\textsuperscript{#1}}

@@

After the model setting we set a series of condition that create the signal. Such condition are highlighted in the following flowchart.

\begin{tikzpicture}[
node distance= 7mm and 13 mm,
     start chain = going below,
     base/.style = {draw, thick, align=center, 
                    inner ysep=1mm, inner xsep=2mm,
                    join=by arrow, on chain},
startstop/.style = {base, rounded rectangle},
       io/.style = {trapezium, base,
                    trapezium left angle=70, trapezium right angle=110},
  process/.style = {base},
 decision/.style = {diamond, aspect=1.5, base, inner xsep=0pt},
    arrow/.style = {-{Stealth[scale=1.0]}, rounded corners, thick}
                    ]
 % main
\node (start) [startstop] {Start};
\node (p1)  [process]   {Buy = FALSE};
\node (d1) [decision]  {$\text{Price} > \text{Prediction} $};

\node (d2) [decision]  {$Price > Prediciton$};
\node (p3)     [process]        {Buy = TRUE};

% left and right
\node (p2f)    [process, left=of d1]   {Buy = TRUE};
\node (p2t)    [process, right=of d1]   {Buy = FALSE};

% coordinates

%
\draw[arrow] (d1.east) node[above left] {True} -- (p2t);
%\draw[arrow] (d1.east) node[above left] {False} -- (p2f);
%\draw[arrow] (d1.west) node[above left] {True} -- (p2t);

\end{tikzpicture}

@@

All the scripts and files are available on GitHub at the following repository:
\href{url}{https://github.com/mrepetto94/DynamicEcon}
